---
title: "`r params$test`  \n`r params$school` `r ifelse(params$teacher == params$school, '', params$teacher)`"
header-includes: 
   \usepackage{fancyhdr}
   \usepackage{graphicx} 
   \usepackage{eurosym} 
   \usepackage{booktabs,xcolor} 
   \pagestyle{fancy} 
   \fancyhf{}
   \fancypagestyle{plain}{\pagestyle{fancy}}
   \addtolength{\headheight}{0.5cm}
   \rhead{`r params$test` Report - \today} 
  
   \fancyfoot[LE,RO]{Page \thepage}
   \usepackage{pdflscape}
   \newcommand{\blandscape}{\begin{landscape}}
   \newcommand{\elandscape}{\end{landscape}}
   \usepackage[default]{lato}
   \usepackage[T1]{fontenc}
output: 
  pdf_document:
    latex_engine: xelatex
always_allow_html: yes
params:
  test_id: "IA.1920.03.ELA.1DL"
  test: "19-20 G3 ELA Interim Assessment 1 - DL Modified"
  teacher: "Sommerio"
  school: "KACP"
---

```{r global_options, include=FALSE}
#  \lhead{\includegraphics[width=4cm]{KIPP Chicago Regional (Dark Blue).eps}}
# \fancypagestyle{plain}{\pagestyle{fancy}}
#\addtolength{\headheight}{0.5cm}
#\rfoot{Page \thepage}

knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```


```{r setup, include=FALSE}
library(ggplot2)
library(gridExtra)
library(formattable)
library(webshot)
library(ggrepel)
library(dplyr)
library(cowplot)
library(grid)
library(gridGraphics)
library(DT)
library(here)
library(stringr)
# load(here("data/1819_dl_IA_3.Rda"))
load(here("data/1920_dl_IA_1.Rda"))
source(here("lib/17_18_ia_dl_helpers.R"))
```

## 19-20 Goals 
In the spirit of grounding us in an ambitious bar for students, we will use 70% as mastery/proficiency on end of modules and IAs.  

  * 100% of students demonstrate mastery/proficiency of focus standards (70% or above)
  * 80% of students demonstrate mastery of all standards (70% or above)
  * 0% of students in the lowest performance band 
\
\

```{r all_data}



```
\
\

**Table 1. Grade Level View**  
**Assessment: `r params$test`**  
This table displays the average percent correct on each grade level assessment by school.  

```{r grade_level_view_data} 
#need test param
grade_view_data_0 <- assess_summary_school_sped %>%
  ungroup() %>% 
  select(-c(assessment_id,
            total_pts,
            pts_scored)) %>%
  dplyr::filter(grepl(params$test_id, local_assessment_id)) %>%
  tidyr::spread(key = teacher_name,
                value = pct_correct) %>%
  inner_join(assess_summary_region_sped %>%
               ungroup() %>% 
               select(local_assessment_id,
                      #grade_level,
                      reg_pct_correct),
             by = "local_assessment_id") %>% 
  rename(Region = reg_pct_correct)


grade_view_data <- grade_view_data_0 %>%
  #dplyr::filter(title == params$test) %>% #"Copy of 17-18 G5 Math Interim Assessment 1.v2"
  select(-local_assessment_id) %>%
  rename(Assessment = title)


dt_grade_level_view_dl(grade_view_data)

```
\
\

**Legend**
```{r legend, out.width="300pt"}
legend <- tribble(
  ~pct, ~expectations,
  "0 - 20%", "Did Not Yet Meet Expectations",
  "21% - 40%", "Partially Met Expectations",
  "41% - 69%", "Approaches Expectations",
  "70% - 80%", "Met Expectations",
  "81% and above", "Exceeds Expectations"
) %>% 
  t()

 

legend %>%
  DT::datatable(rownames = FALSE,
                colnames = NULL,
                 width = "50%",
                 height = "60%",
                 options = list(dom = "t",
                                bSort = FALSE,
                                autoWidth = FALSE,
                                columnDefs = list(
                                  list(width = '50px',
                                       targets = c(0:4)))
                                 )) %>%
  formatStyle(c("V1", "V2","V3", "V4", "V5"),
                backgroundColor = styleEqual( c(legend[1,], legend[2,]),
                                              c("#FF001A", #red
                                                "#FFBF42", #orange
                                                "#FEFE56", #yellow
                                                "#91FD57", #light green
                                                "#00CA3F", #green
                                                "#FF001A", #red
                                                "#FFBF42", #orange
                                                "#FEFE56", #yellow
                                                "#91FD57", #light green
                                                "#00CA3F" #green
))
              ) %>%
  formatStyle(c("V1", "V2","V3", "V4", "V5"),
                `font-size` = "12px",
                `font-weight` = "bold",
                `font-family` = "Calibri") 
  
```

\newpage 

**Table 2. Standards View**  
**Assessment: `r params$test`**  
This table displays the average percent correct scored on each standard across school/teacher.  
 
```{r standards_view, out.height="300pt"}
#need test param
grade_level_std <- stds_mastered_by_student_sped %>%
  dplyr::filter(grepl(params$test_id, local_assessment_id)) %>% #"Copy of 17-18 G5 Math Interim Assessment 1.v2"
  group_by(teacher_name,
         title,
         custom_code,
         number_of_questions) %>% 
  summarise(total_points = sum(points),
            total_pts_possible = sum(points_possible),
            pct_correct = total_points/total_pts_possible) %>% 
  select(-c(total_points,
            total_pts_possible)) %>% 
  tidyr::spread(key = teacher_name,
                value = pct_correct) %>% 
  left_join(stds_mastered_by_student_sped %>% 
              ungroup() %>% 
              select(title,
                     custom_code) %>% 
              unique(),
            by = c("title",
                   "custom_code"))

region_stds_view <- stds_mastered_by_student_sped %>% 
  dplyr::filter(grepl(params$test_id, local_assessment_id)) %>% #"Copy of 17-18 G5 Math Interim Assessment 1.v2"
  group_by(custom_code) %>% 
  summarise(reg_total_pts = sum(points), 
            reg_total_possible = sum(points_possible), 
            reg_pct_correct = reg_total_pts/reg_total_possible) %>%
  ungroup() %>%
  select(custom_code,
         reg_pct_correct)

stds_grade_region <- grade_level_std %>% 
  inner_join(region_stds_view,
             by = "custom_code")

  
grade_stds_view <- stds_grade_region %>% 
  ungroup() %>% 
  select(-title) %>% 
  rename(Standards = custom_code,
         `Number of Items` = number_of_questions,
         Region = reg_pct_correct)

dt_stds_view_dl(grade_stds_view)

```

\newpage

**Table 3a. Percent Not Yet Mastered**  
**Assessment: `r params$test`**  
This table displays the percent of students by school and region scoring in the bottom performance band (averaged 20% or less on the assessment).  
\
```{r not_yet_mastered, out.height="300pt"}
assess_summary_school_sped %>% 
  ungroup() %>% 
  select(local_assessment_id,
         title,
         teacher_name) %>% 
  unique() %>% 
  left_join(bottom_band_sped,
            by = c("local_assessment_id",
                   "title",
                   "teacher_name")) %>% 
  mutate(btm_band = if_else(is.na(btm_band), 0, as.double(btm_band))) %>% 
  filter(grepl(params$test_id, local_assessment_id)) %>% 
  tidyr::spread(teacher_name,
                btm_band) %>% 
  left_join(region_btm_band_sped %>%
              ungroup() %>% 
              select(title,
                     Region = reg_pct),
            by = "title") %>% 
  ungroup() %>% 
  select(-c(local_assessment_id)) %>% 
  rename(Assessment = title) %>% 
  not_yet_mastered()
```
\
\
**Table 3b. Percent Mastered**  
**Assessment: `r params$test`**   
Below is the percent of students that mastered (scored 70% or above) each standard.  
\
```{r mastered, out.height="300pt"}
stds_mastered_by_student_sped %>% 
  ungroup() %>% 
  filter(grepl(params$test_id, local_assessment_id)) %>% 
  select(local_assessment_id,
         title,
         teacher_name,
         custom_code) %>% 
  unique() %>% 
  left_join(mastered_band_sped %>% 
              filter(grepl(params$test_id, local_assessment_id)),
            by = c("local_assessment_id",
                   "title",
                   "teacher_name",
                   "custom_code")) %>% 
  mutate(mastered_band = if_else(is.na(mastered_band), 0, as.double(mastered_band))) %>% 
  tidyr::spread(teacher_name,
                mastered_band) %>% 
  left_join(region_m_band_sped %>%
              ungroup() %>% 
              select(title,
                     custom_code,
                     Region = reg_pct),
            by = c("title",
                   "custom_code")) %>% 
  ungroup() %>% 
  select(-c(local_assessment_id,
            title)) %>% 
  rename(Standards = custom_code) %>% 
  mastered()
```

\newpage

**Graph 1. Standards Mastered Grade Level View**  
This graph displays the mastery level of students for each standard.  

```{r hist_student_names, fig.height=15, dev = "cairo_pdf"}
list_standards <- stds_mastered_by_student_sped %>%
  dplyr::filter(grepl(params$test_id, local_assessment_id), 
                grepl(params$teacher, teacher_name)
               ) %>%
  select(custom_code) %>%
  arrange(custom_code) %>%
  unique()

stds_mastery_grade_data <-
  stds_mastered_by_student_sped %>%
  dplyr::filter(grepl(params$test_id, local_assessment_id), 
                grepl(params$teacher, teacher_name)
               ) %>%
  mutate(mastered_level = factor(mastered_level, 
                                 levels = c("Mastered",
                                            "Near Mastery",
                                            "Partially",
                                            "Not Yet Mastered"))) %>%
  mutate(firstlast = str_c(first_name, last_name, sep = " ")) 

  
  # tidyr::unite(firstlast, 
  #              first_name, 
  #              last_name, 
  #              sep = " ") 

middle_name_join <- function(file) {
  repeats <- file %>% 
    group_by(local_student_id, firstlast) %>%
    summarize() %>%
    ungroup() %>%
    select(-local_student_id) %>%
    count(firstlast) %>%
    filter(n > 1)
  
  file <- file %>% 
    filter(firstlast == repeats$firstlast) %>%
    mutate(middlefirstlast = str_c(first_name, middle_name, last_name, sep = " "))
  
  return(file)
  
}

middle_name_join_file <- middle_name_join(stds_mastery_grade_data)

stds_mastery_grade_data <- stds_mastery_grade_data %>%
  left_join(middle_name_join_file %>%
              select(local_student_id, middlefirstlast), 
            by = "local_student_id") %>% 
  mutate(firstlast = ifelse(is.na(middlefirstlast), firstlast, middlefirstlast)) %>% 
  select(-middlefirstlast) %>%
  group_by(#home_room, 
           teacher_name,
           custom_code, 
           mastered_level) %>%
  unique() %>%
  mutate(pct_rank = row_number(percent_correct))

# bringing in middle name for two students with same first and last name on same test

n_stds <- nrow(list_standards)
pages <- ceiling(n_stds / 4)
cut_off <- ceiling(n_stds/pages)

print_hr_stds_table <- function(stds_cut_off) {
  cat(sprintf("**%s - %s** \n ", params$teacher, params$test),
      sep = "\n")
print(stds_mastered_grade_level_dl(stds_mastery_grade_data %>%
                            dplyr::filter(custom_code %in% list_standards$custom_code[1:stds_cut_off])))
cat("\\newpage")
cat("\n")

if(n_stds > stds_cut_off &
   n_stds < stds_cut_off*2){
 cat(sprintf("**%s - %s** \n ", params$teacher, params$test),
      sep = "\n")
  print(stds_mastered_grade_level_dl(stds_mastery_grade_data %>%
                            dplyr::filter(custom_code %in% list_standards$custom_code[stds_cut_off+1:n_stds])))
}

if(n_stds >= (stds_cut_off*2)){
cat(sprintf("**%s - %s** \n ", params$teacher, params$test),
      sep = "\n")
  print(stds_mastered_grade_level_dl(stds_mastery_grade_data %>%
                            dplyr::filter(custom_code %in% list_standards$custom_code[(stds_cut_off+1):(stds_cut_off*2)])))

cat("\\newpage")
cat("\n")
}

if(n_stds > (stds_cut_off*2) &
     n_stds <= (stds_cut_off*3)){
cat(sprintf("**%s - %s** \n ", params$teacher, params$test),
      sep = "\n")
  print(stds_mastered_grade_level_dl(stds_mastery_grade_data %>%
                            dplyr::filter(custom_code %in% list_standards$custom_code[((stds_cut_off*2)+1):n_stds])))
cat("\\newpage")
cat("\n")
  } else if(n_stds > (stds_cut_off*3)){
    cat(sprintf("**%s - %s** \n ", params$teacher, params$test),
      sep = "\n")
  print(stds_mastered_grade_level_dl(stds_mastery_grade_data %>%
                            dplyr::filter(custom_code %in% list_standards$custom_code[((stds_cut_off*2)+1):(stds_cut_off*3)])))
cat("\\newpage")
cat("\n")
  }

 if(n_stds > (stds_cut_off*3) &
     n_stds <= (stds_cut_off*4)){
cat(sprintf("**%s - %s** \n ", params$teacher, params$test),
      sep = "\n")
  print(stds_mastered_grade_level_dl(stds_mastery_grade_data %>%
                            dplyr::filter(custom_code %in% list_standards$custom_code[((stds_cut_off*3)+1):n_stds])))
cat("\\newpage")
cat("\n")
 }else if(n_stds > (stds_cut_off*4)){
    cat(sprintf("**%s - %s** \n ", params$teacher, params$test),
      sep = "\n")
  print(stds_mastered_grade_level_dl(stds_mastery_grade_data %>%
                            dplyr::filter(custom_code %in% list_standards$custom_code[((stds_cut_off*3)+1):(stds_cut_off*4)])))
cat("\\newpage")
cat("\n")
  }
  
if(n_stds > (stds_cut_off*4) &
     n_stds <= (stds_cut_off*5)){
cat(sprintf("**%s - %s** \n ", params$teacher, params$test),
      sep = "\n")
  print(stds_mastered_grade_level_dl(stds_mastery_grade_data %>%
                            dplyr::filter(custom_code %in% list_standards$custom_code[((stds_cut_off*4)+1):n_stds])))
cat("\\newpage")
cat("\n")
 } else if(n_stds > (stds_cut_off*5)){
  cat(sprintf("**%s - %s** \n ", params$teacher, params$test),
      sep = "\n")
  print(stds_mastered_grade_level_dl(stds_mastery_grade_data %>%
                            dplyr::filter(custom_code %in% list_standards$custom_code[((stds_cut_off*4)+1):(stds_cut_off*5)])))
cat("\\newpage")
cat("\n")
 }

# if(n_stds >= (stds_cut_off*6)){
# cat(sprintf("**%s - %s** \n ", params$teacher, params$test),
#       sep = "\n")
#   print(stds_mastered_grade_level_dl(stds_mastery_grade_data %>%
#                             dplyr::filter(custom_code %in% list_standards$custom_code[((stds_cut_off*5)+1):(stds_cut_off*6)])))
# cat("\\newpage")
# cat("\n")
# } 
# 
# if(n_stds >= (stds_cut_off*7)){
# cat(sprintf("**%s - %s** \n ", params$teacher, params$test),
#       sep = "\n")
#   print(stds_mastered_grade_level_dl(stds_mastery_grade_data %>%
#                             dplyr::filter(custom_code %in% list_standards$custom_code[((stds_cut_off*6)+1):(stds_cut_off*7)])))
# cat("\\newpage")
# cat("\n")
# } else{
#    cat(sprintf("**%s - %s** \n ", params$teacher, params$test),
#       sep = "\n")
#   print(stds_mastered_grade_level_dl(stds_mastery_grade_data %>%
#                             dplyr::filter(custom_code %in% list_standards$custom_code[((stds_cut_off*6)+1):n_stds])))
# cat("\\newpage")
# cat("\n")
# }
# 
# if(n_stds >= (stds_cut_off*8)){
# cat(sprintf("**%s - %s** \n ", params$teacher, params$test),
#       sep = "\n")
#   print(stds_mastered_grade_level_dl(stds_mastery_grade_data %>%
#                             dplyr::filter(custom_code %in% list_standards$custom_code[((stds_cut_off*7)+1):(stds_cut_off*8)])))
# cat("\\newpage")
# cat("\n")
# }
}
```

```{r, results = 'asis', fig.height=15, dev = "cairo_pdf"}
print_hr_stds_table(cut_off)

```

\newpage

**Graph 2. Standards Mastered Homeroom View**  
**`r params$teacher` - `r params$test`**  
This graph displays students' mastery level of assessment standards by homeroom. The number of standards not mastered can be easily identified.  

```{r}
number_mastered <- stds_mastery_grade_data %>%
  # dplyr::filter(grepl(params$subject, local_assessment_id),
  #               home_room == list_homerooms$home_room[1]) %>%
  group_by(student_id, firstlast, mastered_level) %>%
  summarise(total_mastered = n()) %>%
  tidyr::spread(key = mastered_level,
                value = total_mastered)

name_ord_0 <-  stds_mastery_grade_data %>% 
  # dplyr::filter(grepl(params$subject, local_assessment_id),
  #               home_room == list_homerooms$home_room[1]) %>%
  ungroup() %>%
  select(custom_code, firstlast, mastered_level, student_id) %>% 
  mutate(m_level_2 = if_else(mastered_level == "Mastered", 3, 
                     if_else(mastered_level == "Near Mastery", 2,
                     if_else(mastered_level == "Partially", 1, 0))))%>%
  select(-mastered_level) %>% 
  unique() %>% 
  tidyr::spread(custom_code, m_level_2)

ss_colnames_0 <- grep("CCSS|DLM", colnames(name_ord_0))

ss_colnames_1 <- colnames(name_ord_0)[ss_colnames_0]

name_ord_1 <- name_ord_0 %>% 
  arrange_(.dots = paste("desc(", ss_colnames_1, ")")) %>%
  select(firstlast)

student_mastery_homeroom(number_mastered, stds_mastery_grade_data, name_ord_1, ss_colnames_1) 
```



