---
title: "Question Analysis"
output: html_document
runtime: shiny
---

#### Identifing average scores for Gen Ed IA items

* Item scores based on KOA students only
* Note some questions could be repeated across years but appear as separate items
* Use the slider under Mean Score (Percent) to filter the range of values and the select under Subject to filter the Subjects shown

```{r global_options, include=FALSE}

bq_auth_file <-Sys.getenv("BQ_AUTH_FILE")

bigrquery::bq_auth(path = bq_auth_file)

library(silounloadr)
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(formattable)
library(dplyr)
library(cowplot)
library(grid)
library(gridGraphics)
library(DT)
library(here)
library(stringr)
library(shiny)
library(shinydashboard)
library(bigrquery)

knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```


```{r, parameters}
# narrowing down to the assessment IDs we need so we can filter on this later

gened_ias <- c(45664,
45663,
45662,
45665,
45667,
70732,
70733,
70504,
70962,
70735,
70965,
70972,
70966,
61095,
61096,
70734,
70731,
70971,
71052,
71184,
71256,
72861,
73363,
73307,
72868,
73667,
73981,
72849,
72850,
72937,
73375,
73361,
73270,
73527,
73388,
73380,
73386,
75169,
75184,
75108,
75194,
75484,
75482,
75604,
75514,
75500,
75501,
75483,
75428,
75558,
75196,
75625,
75198,
93909,
72937,
75169,
79406,
61095,
79674,
75184,
79404,
79405,
73375,
61096,
79403,
70734,
79402,
79401,
75108,
73361,
79400,
70731,
75194,
79399,
79398,
73270,
79397,
71052,
73388,
79678,
75484,
79679,
79680,
73527,
70971,
75482,
79676,
79677,
99390,
70732,
72861,
40826,
34906,
75604,
79716,
79714,
70733,
45662,
40835,
34907,
73363,
75514,
79710,
79711,
79717,
45665,
40836,
34909,
70504,
75500,
73307,
79705,
79706,
79703,
45667,
40837,
72868,
34908,
70962,
75501,
79718,
79700,
79701,
71184,
73380,
79690,
75483,
79691,
79692,
79687,
73386,
75428,
71256,
79689,
79688,
70735,
45669,
45663,
40828,
34901,
75558,
92987,
100516,
73667,
95386,
45668,
75196,
40827,
34904,
70965,
92988,
79695,
79685,
73981,
45666,
40831,
93869,
72849,
75625,
34903,
70972,
100518,
79683,
45664,
40830,
72850,
75198,
34902,
70966,
100519,
79698,
79682)

```

```{r, helpers}
drop_fivetran_cols <- function(data){
  data %>% 
    select(-starts_with("_fivetran"))
}

```


```{r, bq_tables}

fields <- get_illuminate("fields") %>% 
  dplyr::filter(assessment_id %in% gened_ias) %>%
  collect(n = Inf)

field_responses <- get_illuminate("field_responses") %>%
  collect(n = Inf) 

responses <- get_illuminate("responses") %>% 
  collect(n = Inf)

field_standards <- get_illuminate("field_standards") %>%
  collect() %>%
  select(field_id, standard_id)

student_responses <- get_illuminate("students_assessments_responses") %>% 
  dplyr::filter(assessment_id %in% gened_ias) %>%
  collect(n = Inf)

student_assessments <- get_illuminate("students_assessments") %>%
  dplyr::filter(assessment_id %in% gened_ias) %>%
  collect(n = Inf)

students <- get_illuminate("students", "public") %>%
  select(student_id,
         local_student_id) %>%
  collect()

ps_stus <- get_powerschool("students") %>% 
  drop_fivetran_cols %>%
  select(
    studentid = id,
    first_name,
    last_name,
    grade_level,
    schoolid,
    home_room,
    student_number) %>%
  collect()

standards <- get_illuminate("standards", schema = "standards") %>%
  drop_fivetran_cols() %>%
  collect()

assessments <- get_illuminate("assessments") %>% 
  filter(assessment_id %in% gened_ias) %>% 
  collect()

schools <- tibble(schoolid = c(78102, 7810, 400146, 4001462, 400163, 4001802, 400180),
                  school_name = c("Ascend Primary", "Ascend Middle", "Academy", "Academy Primary", "Bloom", "One Primary", "One Academy"),
                  school_abbrev =c("KAP", "KAMS", "KAC", "KACP", "KBCP", "KOP", "KOA"))



```

```{r, munge_fields}

munged_fields <- fields %>%
  select(field_id,
         assessment_id,
         is_rubric,
         max_points = maximum,
         q_order = sheet_label,
        # sheet_responses
        ) %>%
  left_join(field_responses %>%
              select(field_id,
                     points,
                     response_id,
                     ), by = "field_id") %>%
  left_join(field_standards, by = "field_id") %>%
  left_join(standards %>%
              select(standard_id,
                     custom_code), by = "standard_id") %>% 
  select(-standard_id) %>%
  group_by(field_id, assessment_id, is_rubric, max_points, q_order) %>%
  unique() %>% 
  summarise(points = paste(points, collapse = " "),
         response_ids = paste(response_id, collapse = " "),
         all_standards = paste(custom_code, collapse = " ")) %>%
  mutate(question_type = case_when(
    is_rubric == TRUE ~ "Rubric",
    is_rubric == FALSE & nchar(points) == 1 ~ "Multiple Choice",
    is_rubric == FALSE & nchar(points) != 1 ~ "Multiple Select"
  ))

munged_fields$all_standards <- sapply(strsplit(as.character(munged_fields$all_standards), " "), function(x) paste(unique(x), collapse = ", "))

```


```{r, munge_student_responses}

munged_student_responses <- student_responses %>%
  filter(assessment_id %in% gened_ias) %>%
  select(student_assessment_response_id,
         assessment_id,
         field_id,
         student_response_id = response_id,
         student_assessment_id,
         is_deleted = `_fivetran_deleted`) %>%
  filter(is.na(is_deleted)) %>%
  select(-is_deleted) %>%
  left_join(student_assessments %>%
              select(student_assessment_id,
                     assessment_id,
                     student_id), by = c("assessment_id", "student_assessment_id")) %>% 
   select(-c(student_assessment_response_id, student_assessment_id)) %>% unique() %>%
  left_join(students, by = "student_id") %>%
  left_join(ps_stus %>% select(
    studentid,
    local_student_id = student_number, 
    schoolid) %>%
      mutate(local_student_id = as.character(local_student_id)), by = "local_student_id") 
  

```

```{r, combined}

combined_fields_responses <- munged_student_responses %>%
  left_join(munged_fields, by = c("field_id", "assessment_id")) %>% 
  select(student_id,
         assessment_id,
         all_standards,
         q_order,
         question_type,
         max_points,
         correct_response_ids = response_ids,
         points,
         student_response_id,
         schoolid) %>%
  left_join(schools, by = "schoolid") %>%
  filter(schoolid == 999999 | schoolid == 400180)

```

```{r, responses_lookup}

responses_lookup <- combined_fields_responses %>%
  select(assessment_id,
         q_order,
         question_type,
         correct_response_ids,
         points) %>%
  separate_rows(correct_response_ids, points, sep = " ") %>% 
  unique() %>%
  mutate(correct_response_ids = as.integer(correct_response_ids))

```

```{r, student_q_credit}

student_q_credit <- combined_fields_responses %>%
  select(-c(correct_response_ids, points)) %>%
  left_join(responses_lookup %>% rename(student_response_id = correct_response_ids), 
            by = c("assessment_id", "q_order", "question_type", "student_response_id")) %>%
  mutate(points = case_when(
    is.na(points) ~ 0,
    TRUE ~ as.double(points) 
  )) %>%
  mutate(student_credit = points/max_points) %>%
  select(-c(student_response_id)) %>%
  left_join(assessments %>% select(assessment_id, local_assessment_id), 
            by = "assessment_id")

```

```{r, question_analysis}

question_analysis <- student_q_credit %>% 
  group_by(assessment_id, all_standards, q_order, question_type) %>%
  summarize(mean_q_credit = mean(student_credit),
            number_of_students = n()) %>%
  mutate(mean_q_credit = round(mean_q_credit, 3)) %>%
  filter(mean_q_credit != 0) %>%
  ungroup() %>%
  left_join(assessments %>% select(assessment_id, local_assessment_id), 
            by = "assessment_id") %>% 
  mutate(grade_level = as.factor(str_replace(str_extract(local_assessment_id, "03|04|05|06|07|08"), "0", "")),
         question_type = as.factor(question_type),
         subject = as.factor(str_extract(local_assessment_id, "ELA|Math|Science")),
         mean_q_credit = mean_q_credit * 100,
         school_abbrev = "KOA",
         school_year = as.factor(str_extract(local_assessment_id, "1718|1819|1920"))) %>%
  filter(grade_level %in% c(5,6,7,8)) %>%
  select(`School Year` = school_year,
    `Grade Level` = grade_level,
         School = school_abbrev,
         Subject = subject,
         `Assessment ID` = local_assessment_id,
         `Question Order` = q_order,
         `Question Type` = question_type,
         Standards = all_standards,
         `N` = number_of_students,
         `Mean Score (Percent)` = mean_q_credit)

```

```{r}

datatable(question_analysis,
          extensions = 'Buttons',
          filter = 'top', 
          rownames = FALSE, 
          options = list(dom = 'Bfrtip', buttons = c('copy', 'excel'), pageLength = 20))

```



##### The distribution of the mean scores by question type and subject is shown below. Note it does not change with different filters to the data table but will change with different Grade Level inputs selected below



```{r}
# question_analysis %>%
#   ggplot(aes(`Mean Score (Percent)`, fill = Subject), aes = .5) +   
#   kippcolors::scale_fill_kipp(palette = "kipp_qual") +
#   geom_density() +
#   theme_minimal() +
#   labs(title = "Distribution of Student Question Scores") +
#   facet_wrap(vars(`Question Type`))
  
```

```{r}

ui = fluidPage(
  inputPanel(
  selectizeInput("grade", label = "Grade Level", 
              choices = c(5, 6, 7, 8), selected = c(5,6,7,8), multiple = TRUE)),
  
  fluidRow(column(width = 12,
                  plotOutput(outputId = "plot")))
)

server = function(input,output) {
  output$plot = 
  renderPlot({
    question_analysis %>%
      filter(`Grade Level` %in% input$grade) %>%
      ggplot(aes(`Mean Score (Percent)`, fill = Subject)) +   
      kippcolors::scale_fill_kipp(palette = "kipp_qual") +
      geom_density(alpha = .6) +
      theme_minimal() +
      labs(title = "Distribution of Student Question Scores") +
      facet_wrap(vars(`Question Type`))
})

} 
  
#options = list(height = 500)



shinyApp(ui, server, options = list(height = 500))

```


```{r}

# inputPanel(
#   sliderInput("mean_filter", label = "Range of Average Score",
#               min = 0, max = 100, value = 30, step = .05),
# 
#    # checkboxGroupInput(inputId = "grade_check", label = "Grade Level",
#    #                    choices = c(3,4,5,6,7,8), selected = c(3,4,5,6,7,8)),
#   
#   selectizeInput(inputId = "grade_check", label = "Grade Level",
#                                   choices = c(5,6,7,8),
#                                   selected = c(5,6,7,8),
#                                   multiple = TRUE),
#   
# )
# 
# # grade level
# # standards
# # school id
# 
# # DL
# 
# 
#  renderDataTable({
# 
#    datatable(question_analysis %>% filter(`Mean Score (Percent)` <= input$mean_filter &
#                                    `Grade Level` %in% input$grade_check),
#            extensions = 'Buttons',
#            filter = 'top',
#            options = list(dom = 'Bfrtip', buttons = c('copy', 'excel'), pageLength = 10),
#            rownames = FALSE)
#  })
# 
# renderPlot({
#   question_analysis %>%
#     filter(`Mean Score (Percent)` <= input$mean_filter &
#           `Grade Level` %in% input$grade_check) %>%
#     ggplot(aes(x = `Mean Score (Percent)`)) +
#     geom_density(fill = "#17345B") +
#     theme_minimal() +
#     labs(title = "Distribution of Average Question Scores")
# })



```


```{r}
# 
# inputPanel(
#   checkboxGroupInput("loc_assess_id", label = "Assessment ID",
#                      choices = c("KAP", "KAC", "KAMS", "KOA",
#                                  "KBCP", "KACP"), selected = "KOA"),
# 
#   numericInput("q_num", label = "Question Number",
#                min = 1, max = 30, step = 1),
#   
#     selectizeInput(inputId = "school_name",  
#                                   label = "Select School",
#                                   choices = c("KAMS", "KOA", "KBCP", "KAC", 
#                                               "KAP", "KOP", "KACP"),
#                                   selected = c("KAMS", "KOA", "KBCP", "KAC", 
#                                                "KAP", "KOP", "KACP"),
#                                   multiple = TRUE)
# 
# )
# 
# renderPlot({
#   student_q_credit %>%
#     filter(#`Mean Score` <= input$mean_filter,
#            local_assessment_id %in% input$loc_assess_id,
#            q_order == input$q_num,
#            school_abrev %in% input$school_name) %>%
#     ggplot(aes(x = student_credit)) +
#     geom_density(fill = "#BCD631") +
#     theme_minimal() +
#     labs(title = "Distribution of Student Question Scores")# +
#     #coord_cartesian(ylim=c(0, 10))
# })

```



```{r}

#write_csv(question_analysis, "~/Downloads/table.csv")

```


