---
title: "1920 IA 1 Dashboard"

output: 
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes

---

```{r setup, include=FALSE}
library(ggplot2)
library(gridExtra)
library(formattable)
library(webshot)
library(ggrepel)
library(dplyr)
library(cowplot)
library(grid)
library(gridGraphics)
library(DT)
library(here)
library(kippcolors)
library(stringr)

knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path=here('graphs/'),
                      echo=FALSE, warning=FALSE, message=FALSE)

#load(here("data/1819_IA_2.Rda"))
# load(here("1819_dl_IA_3.Rda"))
# load(here("1819_IA_3_primary.Rda"))
load(here("data/1920_IA_1.Rda"))
load(here("data/1920_dl_IA_1.Rda"))

mid_string <- c("KAC", "KAMS", "KBCP", "KOA")
middle <- enquo(mid_string)
pri_string <- c("KACP", "KAP", "KOP")
primary <- enquo(pri_string)
```



```{r}
subjects <- paste("ELA",
              "Math",
              "Science",
              "Algebra",sep = "|")


ia_5_8_table <- regional_school_rollup %>% 
  mutate(grade_level = stringr::str_extract(local_assessment_id, "0\\d"),
         grade_level = as.double(grade_level),
         subject = stringr::str_extract(local_assessment_id, subjects)) %>% 
  filter(grade_level > 4) %>% 
  tidyr::unite(Assessment, subject, grade_level, sep = " ") %>% 
  mutate(Target = .70) %>% 
  select(Assessment,
         Target,
         Region = reg_pct_correct,
         !!middle) %>% 
  bind_rows(pct_correct_school %>% 
  ungroup() %>% 
  select(-schoolid) %>% 
  tidyr::spread(key = school_abbrev,
                value = school_pct) %>% 
    filter(grepl("05-8", subject)) %>% 
    rename(Assessment = subject) %>% 
    mutate(Target = .70) %>% 
    left_join(pct_correct_reg,
              by = c("Assessment" = "subject"))) %>% 
  arrange(Assessment) %>% 
  select(-!!primary)
  
db_table <- function(ia_table){
  col_names <- colnames(ia_table)
  ia_table %>% 
  DT::datatable(rownames = FALSE,
                  # width = "400px",
                  # height = "300px",
                  options = list(
                    pageLength = nrow(ia_table),
                    dom = "t",
                    bSort = FALSE,
                    autoWidth = TRUE
                    # columnDefs = list(list(
                    #   width = '100px', 
                    #   targets = col_names))
                  )) %>%
    formatStyle(col_names[-c(1,2)],
                background = styleInterval(c(.55, .70),
                                           c("#fc8d59", 
                                             #"#FF001A", #red
                                             "white",
                                           "#99d594")
                                           #"#00CA3F") #green
                ))  %>%
    # formatStyle(col_names,
    #             `font-size` = c('18px')
    # ) %>%
    formatPercentage(col_names[-1], 2) %>%
    formatStyle(col_names, `font-family` = "Lato")

}
  


db_table_b_band <- function(ia_table){
  col_names <- colnames(ia_table)
  ia_table %>% 
  DT::datatable(rownames = FALSE,
                  # width = "400px",
                  # height = "300px",
                  options = list(
                    pageLength = nrow(ia_table),
                    dom = "t",
                    bSort = FALSE,
                    autoWidth = TRUE,
                    columnDefs = list(list(
                      className = "dt-right",
                      targets = 3))
                  )) %>%
    formatStyle(col_names[-c(1,2)],
                color = styleEqual(0, rgb(0,202/255,63/255)
                                   )
                )  %>%
    # formatStyle(col_names,
    #             `font-size` = c('18px')
    # ) %>%
    formatPercentage(col_names[c(-1,-4)], 2) %>%
    formatStyle(col_names, `font-family` = "Lato")

}

ia_3_4_table <- #p_regional_school_rollup %>% 
  # filter(ia > 1) %>% 
  # select(-ia) %>% 
  regional_school_rollup %>% 
  mutate(grade_level = stringr::str_extract(local_assessment_id, "0\\d"),
         grade_level = as.double(grade_level),
         subject = stringr::str_extract(local_assessment_id, "ELA|Math")) %>% 
  filter(grade_level < 5) %>% 
  tidyr::unite(Assessment, subject, grade_level, sep = " ") %>% 
  mutate(Target = .70) %>% 
  select(Assessment,
         Target,
         Region = reg_pct_correct,
         !!primary) %>% 
  bind_rows(#p_pct_correct_school %>% 
              # filter(ia > 1) %>% 
              # select(-ia) %>% 
             pct_correct_school %>% 
               filter(grepl("03-4", subject)) %>% 
              ungroup() %>% 
              select(-schoolid) %>% 
              tidyr::spread(key = school_abbrev,
                value = school_pct) %>% 
              rename(Assessment = subject) %>% 
              mutate(Target = .70) %>% 
              left_join(#p_pct_correct_reg %>% 
                          # filter(ia > 1) %>% 
                          # select(-ia),
                        pct_correct_reg,
              by = c("Assessment" = "subject"))) %>% 
  arrange(Assessment) %>% 
  mutate(Assessment = gsub("00", "", Assessment))


all_ela <- ia_3_4_table %>% 
  filter(grepl("ELA", Assessment)) %>% 
  bind_rows(ia_5_8_table %>% 
  filter(grepl("ELA", Assessment)))


```

## Overall Percent Correct
### ELA

Note that KACP 4th took the 3rd grade ELA assessment

```{r}
all_ela %>% 
  filter(grepl("3|4", Assessment)) %>% 
  select(-!!middle) %>% 
  db_table()

all_ela %>%
  filter(!grepl("3|4", Assessment)) %>%
  select(-!!primary) %>%
  db_table()

```

\
\

### Math

```{r}
ia_3_4_table %>% 
  filter(grepl("Math", Assessment)) %>% 
  db_table()
ia_5_8_table %>% 
  filter(grepl("Math|Algebra", Assessment)) %>% 
  db_table()

  # db_table()
```

\
\

### Science

```{r}
ia_5_8_table %>% 
  filter(grepl("Sci", Assessment)) %>% 
  db_table()
```

```{r sped}

sped_table <- sped_grade_reg %>% 
  mutate(Target = 0.7) %>% 
  #filter(grade_level > 4) %>% 
  mutate(Assessment = sprintf("DL %s %s", subject, grade_level)) %>% 
  ungroup() %>% 
  select(Assessment, 
         Target,
         Region,
         !!primary,
         !!middle) %>% 
  bind_rows(sped_school_subject %>% 
  tidyr::spread(school_abbrev,
                pct_correct) %>%
  left_join(sped_region,
            by = "subj_grade") %>% 
  mutate(Target = .7) %>%
  ungroup() %>% 
  select(Assessment = subj_grade,
         Target,
         Region = reg_pct_correct,
         !!primary,
         !!middle)) %>% 
  arrange(Assessment)

```

\
\

### DL ELA

```{r}
sped_table %>% 
  filter(grepl("ELA", Assessment),
         grepl("3|4", Assessment)) %>% 
  select(-!!middle) %>% 
  db_table()

sped_table %>% 
  filter(grepl("ELA", Assessment),
         !grepl("3|4", Assessment)) %>% 
  select(-!!primary) %>% 
  db_table()
```

\
\

### DL Math

```{r}
 sped_table %>% 
  filter(grepl("Math", Assessment),
         grepl("3|4", Assessment)) %>% 
  select(-!!middle) %>% 
  db_table()

sped_table %>% 
  filter(grepl("Math", Assessment),
         !grepl("3|4", Assessment)) %>% 
  select(-!!primary) %>% 
  db_table()
```

\
\

## Not Yet Mastered

**Percent of students in lowest perfomance band (averaged < 21% on the IA)**  

* KOP had 1 student that scored in the lowest performance band across all tests in their first year administering IAs
* DL students at KAP had 0 scores in the lowest performance band in both Math and ELA
* KOA had at least two grade levels with 0 students in the lowest performance band in all subjects
* KBCP had at least one grade level with 0 students in the lowest performance band in both gen ed Math and ELA

\
```{r out.width= "300pt"}
school_region <- bottom_band_school_sub %>% 
    tidyr::spread(school_abbrev,
                  school_pct_btm_band) %>% 
    left_join(bottom_band_reg,
              by = "subject") %>% 
    rename(Region = subj_pct_btm_band) %>% 
    mutate(Assessment = subject,
           Target = 0) %>% 
    select(-subject)

all_low_band <- bottom_band %>% 
  mutate(grade_level = stringr::str_extract(local_assessment_id, "0\\d"),
         grade_level = as.double(grade_level),
         subject = stringr::str_extract(local_assessment_id, "ELA|Math|Science|Algebra")) %>% 
  tidyr::unite(Assessment, subject, grade_level, sep = " ") %>% 
  mutate(Target = 0) %>% 
  ungroup() %>% 
  select(Assessment,
         Target,
         Region = reg_pct,
         !!primary,
         !!middle) %>% 
 # mutate(KAC = ifelse(Assessment %in% "Math 5", NA, KAC)) %>% 
  bind_rows(school_region) %>% 
  arrange(Assessment)

n_btm_band_subj <- n_btm_band_grade %>% 
  mutate(subject = gsub("3|4", "03-4", subject),
         subject = gsub("[5-8]", "05-8", subject)) %>% 
  group_by(subject) %>% 
  summarize(not_yet = sum(not_yet),
            n_students = sum(n_students)) %>% 
  mutate(N = sprintf("%s/%s", not_yet, n_students)) %>% 
  select(-not_yet,
         -n_students)
  
n_btm_band <- n_btm_band_grade %>% 
  group_by(subject) %>% 
  summarize(not_yet = sum(not_yet),
            n_students = sum(n_students)) %>% 
  mutate(N = sprintf("%s/%s", not_yet, n_students)) %>% 
  select(-not_yet,
         -n_students) %>% 
  bind_rows(n_btm_band_subj) %>% 
  rename(Assessment = subject)
```

### ELA

* 6th ELA had just 5 students in the lowest performance band
* No school had more than 15% of their students in the lowest performance band for an ELA assessment

```{r}
all_low_band %>% 
  filter(grepl("ELA (03|[3-4])", Assessment)) %>% 
  left_join(n_btm_band,
            by = "Assessment") %>% 
  select(Assessment:Region,
         N,
         !!primary) %>% 
  db_table_b_band()

all_low_band %>% 
  filter(grepl("ELA (05|[5-8])", Assessment)) %>% 
  left_join(n_btm_band,
            by = "Assessment") %>% 
  select(Assessment:Region,
         N,
         !!middle) %>% 
  db_table_b_band()
```

\
\

### Math

* Less than 1% of all 6th graders were in the lowest performance band, the lowest regional percentage for all gen ed IAs
* 5th Math at KAMS had no students in the lowest performance band

```{r}
all_low_band %>% 
  filter(grepl("Math (03|[3-4])", Assessment)) %>% 
  left_join(n_btm_band,
            by = "Assessment") %>% 
  select(Assessment:Region,
         N,
         !!primary) %>% 
  db_table_b_band()

all_low_band %>% 
  filter(grepl("Algebra|Math (05|[5-8]|)", Assessment)) %>% 
  left_join(n_btm_band,
            by = "Assessment") %>% 
  select(Assessment:Region,
         N,
         KAC:KOA,
         -KAP) %>% 
  distinct() %>%
  filter(!grepl("th 3|th 4|03-4", Assessment)) %>%
  db_table_b_band()

```

\
\

### Science

* KOA had no students in the lowest performance band across all grades in Science
* All grade levels and schools had less than 10 students score in the lowest performance band

```{r}
all_low_band %>% 
  filter(grepl("Sci", Assessment)) %>% 
  left_join(n_btm_band,
            by = "Assessment") %>% 
  select(Assessment:Region,
         N,
         !!middle) %>% 
  db_table_b_band()
  
```

\
\


```{r}

sped_low_band <- sped_grade_b_band %>% 
  tidyr::spread(school_abbrev,
                pct) %>% 
  ungroup() %>% 
  tidyr::unite(Assessment, subject, grade_level, sep = " ") %>% 
  left_join(sped_reg_b_band %>% 
              tidyr::unite(Assessment, subject, grade_level, sep = " ") %>% 
              rename(Region = pct),
            by = "Assessment") %>% 
  bind_rows(sped_school_b_band %>% 
              tidyr::spread(school_abbrev,
                            pct) %>% 
              left_join(sped_reg_grade_b_band %>% 
                          rename(Region = pct),
              by = "subject") %>% 
              rename(Assessment = subject)) %>% 
  arrange(Assessment) %>% 
   mutate(Assessment = sprintf("DL %s", Assessment),
          Target = .0)
 
```

\
\

### DL ELA

* Regionwide, 8th Grade only had one student score in the lowest band
* KAC 6th and 7th DL ELA had 0 students in the lowest band

```{r}
n_dl_reg <- sped_school_b_band_0 %>% 
  group_by(subject) %>% 
  summarize(not_yet = sum(not_yet),
            n_students = sum(n_students)) %>% 
  mutate(N = sprintf("%s/%s", not_yet,n_students),
         subject = sprintf("DL %s", subject)) %>% 
  select(-c(not_yet,
            n_students))

n_dl_subj <- sped_grade_b_band_0 %>%  #need to find n students out of total 
  ungroup() %>% 
  mutate(subject = sprintf("DL %s %s", subject, grade_level)) %>% 
  select(-n_students,
         -grade_level,
         -schoolid,
         -pct) %>% 
  right_join(total_students_sped_0,
             by = c("subject",
                    "school_abbrev")) %>% 
  mutate(not_yet = if_else(is.na(not_yet), 0, as.double(not_yet))) %>% 
  group_by(subject) %>% 
  summarize(not_yet = sum(not_yet),
            n_students = sum(n_students)) %>%
  mutate(N = sprintf("%s/%s", not_yet, n_students)) %>%
  select(subject, N)
  
  
n_dl <- n_dl_reg %>% 
  bind_rows(n_dl_subj)
  
sped_low_band %>% 
  filter(grepl("ELA", Assessment),
         grepl("3|4", Assessment)) %>% 
  left_join(n_dl,
            by = c("Assessment" = "subject")) %>% 
  select(Assessment,
         Target,
         Region,
         N, 
         !!primary) %>% 
  db_table_b_band()

sped_low_band %>% 
  filter(grepl("ELA (05|[5-8])", Assessment)) %>% 
  left_join(n_dl,
            by = c("Assessment" = "subject")) %>% 
  select(Assessment,
         Target,
         Region,
         N, 
         !!middle) %>% 
  db_table_b_band()
```

\
\

### DL Math

* No 5th through 7th grade KOA student that took the DL Math assessment scored in the lowest performance band

```{r}
sped_low_band %>% 
  filter(grepl("Math (03|[3-4])", Assessment)) %>% 
  left_join(n_dl,
            by = c("Assessment" = "subject")) %>% 
  select(Assessment,
         Target,
         Region,
         N, 
         !!primary) %>% 
  db_table_b_band()

sped_low_band %>% 
  filter(grepl("Math (05|[5-8])", Assessment)) %>% 
  left_join(n_dl,
            by = c("Assessment" = "subject")) %>% 
  select(Assessment,
         Target,
         Region,
         N, 
         !!middle) %>% 
  db_table_b_band()
```

\
\

## Graph - Not Yet Mastered

**Percent of students in the lowest performance band**
 
* 53% of IAs have less than 6% of students that took the assessment in the bottom performance band.  
* 3rd and 4th DL Math and ELA have 1 student in the bottom band across the region
* 7 IAs have three or fewer students in the bottom band

```{r}
low_bands_all_0 <- all_low_band %>% 
  bind_rows(sped_low_band) %>% 
  filter(!grepl("03-4|05-8", Assessment)) %>% 
  mutate(grade = stringr::str_extract(Assessment, "\\d"),
         Assessment = gsub(" \\d", "", Assessment)) %>% 
  mutate(assessment = sprintf("%sth %s", grade, Assessment)) %>% 
  select(assessment, Region) #%>% 
  # filter(!assessment %in% c("4th DL ELA", "4th DL Math"))

order_ias <-  low_bands_all_0 %>% 
  mutate(assessment = ifelse(grepl("3th", assessment), str_replace_all(assessment, "3th", "3rd"), assessment)) %>%
  arrange(Region) %>%
  distinct()

low_bands_all_0 %>% 
  mutate(assessment = ifelse(grepl("3th", assessment), str_replace_all(assessment, "3th", "3rd"), assessment)) %>%
  distinct() %>%
  mutate(assessment = factor(assessment, levels = order_ias$assessment)) %>% 
  mutate(percent = Region *100) %>% 
  ggplot() +
  geom_bar(aes(x = assessment, 
               y = Region,
               fill = assessment),
           stat = "identity") +
  geom_hline(yintercept = .05,
             size = 5,
             color = "gray") +
  scale_fill_kipp("kipp_div", reverse = FALSE)+
  scale_y_continuous(name = "% of students in lowest performance band") +
  scale_x_discrete(name = "IA") +
  theme_kipp_light() +
  theme(axis.line = element_line(colour = "white"),
        axis.text.x = element_text(angle = 45),
        legend.position = "none")
  
```

