---
title: "SY 19-20 Interim Assessment 2  \n`r params$school` `r params$subject` `r params$grade`th Grade"
header-includes: \usepackage{fancyhdr} \usepackage{graphicx} \usepackage{eurosym}
  \usepackage{booktabs,xcolor} \pagestyle{fancy} \fancyhf{} \fancypagestyle{plain}{\pagestyle{fancy}}
  \addtolength{\headheight}{0.5cm} \rhead{`r params$subject` `r paste0(params$grade,
  'th Grade')` Interim Assessment Report - \today} 
  
    \fancyfoot[LE,RO]{Page \thepage} \usepackage{pdflscape}
  \newcommand{\blandscape}{\begin{landscape}} \newcommand{\elandscape}{\end{landscape}}
  \usepackage[default]{lato} \usepackage[T1]{fontenc}
output:
  pdf_document:
    latex_engine: xelatex
  html_document:
    df_print: paged
params:
  grade: 6
  school: KAC
  subject: Math
always_allow_html: yes
---

```{r global_options, include=FALSE}

# \lhead{\includegraphics[width=4cm]{KIPP Chicago Regional (Dark Blue).eps}}

# \usepackage[T1]{fontenc}
#    \usepackage[default]{raleway}

# \usepackage{fourier} 
#    \usepackage[no-math]{fontspec} 
#    \setsansfont{Optima}


   # \usepackage[T1]{fontenc}
   # \renewcommand*\familydefault{\sfdefault}
   # \usepackage{palatino}
   # \renewcommand{\familydefault}{\sfdefault}
   # \fontfamily{ppl}\selectfont
#\usepackage[sfdefault]{ClearSans}
  
# \fancypagestyle{plain}{\pagestyle{fancy}}
#\addtolength{\headheight}{0.5cm}
#\rfoot{Page \thepage}
library(ggplot2)
library(gridExtra)
library(formattable)
library(webshot)
library(ggrepel)
library(dplyr)
library(cowplot)
library(grid)
library(gridGraphics)
library(DT)
library(here)
library(stringr)

knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path=here('graphs/'),
                      echo=FALSE, warning=FALSE, message=FALSE)
```


```{r setup, include=FALSE}
load(here("data/1920_IA_1.Rda"))
#data/1718_IA_1.Rda
# if(params$grade <= 4){
source(here("lib/18_19_primary_helpers.R"))
# } else{
# source(here("lib/17_18_ia_helpers.R"))
# }

mid_string <- c("KAC", "KAMS", "KBCP", "KOA")
middle <- enquo(mid_string)
pri_string <- c("KACP", "KAP", "KOP")
primary <- enquo(pri_string)
```

## 19-20 Goals  
In the spirit of grounding us in an ambitious bar for students, we will use 70% as mastery/proficiency on end of modules and IAs.  
(Note: this is an increase from 60% from SY 16-17 AND as aligned to PARCC as we can be without more transparency from PARCC.) 

  * 100% of students demonstrate mastery/proficiency of focus standards (70% or above)
  * 80% of students demonstrate mastery of all standards (70% or above)
  * 0% of students in the lowest performance band 
\
\


**Table 1 Average Percent Correct**  
**`r full_name_subj(params$subject)`**    
This table displays the average percent correct scored on Reading for each `r full_name_subj(params$subject)` grade level assessment.
\

```{r overall}
reg_grades <- regional_school_rollup %>%
  mutate(grade_level = as.double(str_extract(local_assessment_id,"0\\d"))) %>% 
  rename(Region = reg_pct_correct)

if(params$grade <= 4){
  reg_grades_filter <- reg_grades %>% 
    filter(grade_level < 5) %>% 
    select(local_assessment_id,
           !!primary,
           Region,
           grade_level)
}else{
  reg_grades_filter <- reg_grades %>% 
    filter(grade_level > 4) %>% 
    select(-!!primary)
}

tab1_avg_mastery <- reg_grades_filter %>%
  dplyr::filter(grepl(params$subject, local_assessment_id)) %>%
  select(-local_assessment_id) %>%
  tidyr::gather(school, pct_correct, -grade_level) %>%
  tidyr::spread(grade_level, pct_correct) 


dt_avg_mastery(tab1_avg_mastery) 
```

\
\

**Legend**
```{r legend, out.width= "300pt"} 
#px
legend <- tribble(
  ~pct, ~expectations,
  "0 - 20%", "Did Not Yet Meet Expectations",
  "21% - 40%", "Partially Met Expectations",
  "41% - 69%", "Approaches Expectations",
  "70% - 80%", "Met Expectations",
  "81% and above", "Exceeds Expectations"
) %>% 
  t()

 

legend %>%
  DT::datatable(rownames = FALSE,
                colnames = NULL,
                 width = "50%",
                 height = "60%",
                 options = list(dom = "t",
                                bSort = FALSE,
                                autoWidth = FALSE,
                                columnDefs = list(
                                  list(width = '50px',
                                       targets = c(0:4)))
                                 )) %>%
  formatStyle(c("V1", "V2","V3", "V4", "V5"),
                backgroundColor = styleEqual( c(legend[1,], legend[2,]),
                                              c("#FF001A", #red
                                                "#FFBF42", #orange
                                                "#FEFE56", #yellow
                                                "#91FD57", #light green
                                                "#00CA3F", #green
                                                "#FF001A", #red
                                                "#FFBF42", #orange
                                                "#FEFE56", #yellow
                                                "#91FD57", #light green
                                                "#00CA3F" #green
))
              ) %>%
  formatStyle(c("V1", "V2","V3", "V4", "V5"),
                `font-size` = "12px",
                `font-weight` = "bold",
                `font-family` = "Lato") 
  
```

\newpage

**Table 2. Grade Level View**  
**Grade: `r params$grade`**  
**`r full_name_subj(params$subject)`**  
This table displays the average percent correct scored on `r full_name_subj(params$subject)` assessments by school and region for a given grade.  
```{r grade_level_view_data, out.width="300pt"} 
#px
grade_view_data <- reg_grades %>%
  dplyr::filter(grade_level == params$grade,
                grepl(params$subject, local_assessment_id)) %>%
  mutate(local_assessment_id = as.character(params$subject)) %>%
  rename(Assessment = local_assessment_id) %>%
  select(-grade_level)

if(params$grade <= 4){
grade_view_data_filter <- grade_view_data %>%
  select(-!!middle)
} else{
  grade_view_data_filter <- grade_view_data %>%
  select(-!!primary)
}

dt_grade_level_view(grade_view_data_filter)

```
\
\

**Table 3. Standards View**  
**Grade: `r params$grade`**  
**`r full_name_subj(params$subject)`**   
This table displays average percent correct scored by `r full_name_subj(params$subject)` standard for a given grade, across all schools and region.  
```{r set_width 1}
if(params$grade <=4){
  o_w <- "350pt"
}else{
  o_w <- "\\textwidth"
}
```

```{r standards_view, out.width= o_w}
grade_level_std <- stds_school_reg %>%
  dplyr::filter(grepl(params$subject, local_assessment_id),
                grade_level == params$grade) %>% #params$grade
  group_by(custom_code, number_of_questions, school) %>%
  summarise(pct_correct = sum(pct_correct)) %>%
  tidyr::spread(key = school,
                value = pct_correct)

region_stds_view <- stds_school_reg %>% 
  dplyr::filter(grepl(params$subject, local_assessment_id),
                grade_level == params$grade) %>% #params$grade
  group_by(grade_level, custom_code) %>% 
  summarise(reg_total_pts = sum(total_pts), 
            reg_n_correct = sum(n_correct), 
            reg_pct_correct = reg_n_correct/reg_total_pts) %>%
  ungroup() %>%
  select(custom_code,
         reg_pct_correct)

stds_grade_region <- grade_level_std %>% 
  inner_join(region_stds_view,
             by = "custom_code")

if(params$grade <= 4){
region_school <- reg_grades %>%
  dplyr::filter(grepl(params$subject, local_assessment_id),
                grade_level == params$grade) %>% #params$grade
  mutate(Standards = "Total") %>%
  select(Standards,
         !!primary,
         Region)
  
grade_stds_view <- region_school %>%
  bind_rows(stds_grade_region %>%
              rename(Standards = custom_code,
                     `Number of Items` = number_of_questions,
                     Region = reg_pct_correct)) %>% 
  filter(!Standards %in% "Total") %>% 
  select(Standards,
         `Number of Items`,
         !!primary,
         Region)

}else{
  region_school <- reg_grades %>%
  dplyr::filter(grepl(params$subject, local_assessment_id),
                grade_level == params$grade) %>% #params$grade
  mutate(Standards = "Total") %>%
  select(Standards,
         c(`KAC`:Region))
  
grade_stds_view <- region_school %>%
  bind_rows(stds_grade_region %>%
              rename(Standards = custom_code,
                     `Number of Items` = number_of_questions,
                     Region = reg_pct_correct)) %>% 
  filter(!Standards %in% "Total") %>% 
  select(Standards,
         `Number of Items`,
         !!middle,
         Region)
}

dt_stds_view(grade_stds_view)

```

\newpage

**Table 4a. Percent Not Yet Mastered**  
**Grade: `r params$grade`**  
**`r full_name_subj(params$subject)`**  
This table displays the percent of students by school and region scoring in the bottom performance band  
(averaged 20% or less on the assessment).  
```{r set_width 2}
if(params$grade <=4){
  o_w <- "300pt"
}else{
  o_w <- "\\textwidth"
}
```

```{r not_yet_mastered, out.width= o_w}

bottom_band_params <- bottom_band %>%
  mutate(grade_level = stringr::str_extract(local_assessment_id, "0\\d"),
         grade_level = as.double(grade_level)) %>% 
  filter(grepl(params$subject, local_assessment_id),
         grade_level == params$grade) %>% 
  mutate(Assessment = params$subject) %>% 
  rename(Region = reg_pct) %>% 
  ungroup() 

if(params$grade <=4){
  bottom_band_filter <- bottom_band_params %>% 
  select(Assessment,
         !!primary,
         Region)
}else{
  bottom_band_filter <- bottom_band_params %>% 
  select(Assessment,
         !!middle,
         Region)
}

bottom_band_filter %>% 
  not_yet_mastered()
```
\
\
**Table 4b. Percent Mastered**  
**Grade: `r params$grade`**  
**`r full_name_subj(params$subject)`**  
Below is the percent of students that mastered (scored 70% or above) each standard.  
```{r set_width 3}
if(params$grade <=4){
  o_w <- "300pt"
}else if(params$grade == 5 & 
    params$subject == "Math"){
  o_w <- "450pt"
}else{
  o_w <- "\\textwidth"
}
```

```{r mastered, out.width= o_w}

mastered_band_params <- mastered_band %>%
  mutate(grade_level = stringr::str_extract(local_assessment_id, "0\\d"),
         grade_level = as.double(grade_level)) %>% 
  filter(grepl(params$subject, local_assessment_id),
         grade_level == params$grade) %>% 
  ungroup() %>% 
  select(-local_assessment_id) %>% 
  rename(Region = reg_pct,
         Standards = custom_code) %>% 
  ungroup() 

if(params$grade <= 4){
  mastered_band_filter <- mastered_band_params %>% 
    select(Standards,
           !!primary,
           Region)
}else{
  mastered_band_filter <- mastered_band_params %>% 
    select(Standards,
           !!middle,
           Region)
}

mastered_band_filter %>% 
  mastered()
```


\newpage

**Graph 1. Average Percent Correct Across Grades**  
This graph shows the average percent correct on `r full_name_subj(params$subject)` grade level assessments across all schools. The vertical line represents the regional average.  
```{r regional_avg_dev}
if(params$grade <= 4){
ord_school <- assess_summary_hr_reg %>%
  ungroup() %>%   
  select(school) %>%
   unique() %>%
  filter(school %in% pri_string) %>% 
   arrange(desc(school))
}else{
  ord_school <- assess_summary_hr_reg %>%
  ungroup() %>%   
  select(school) %>%
   unique() %>%
  filter(school %in% mid_string) %>% 
   arrange(desc(school))
}

avg_pct_line_graph <- reg_grades_filter %>%
  dplyr::filter(grepl(params$subject, local_assessment_id)) %>%
  tidyr::gather(schools, 
                pct_correct, 
                -c(local_assessment_id, 
                   grade_level, 
                   Region)) %>%
   mutate(pct_correct = round(pct_correct * 100,1),
         reg_pct_correct = round(Region * 100,1),
         line_0 = "Regional Average") %>%
   mutate(dot_color_c = ifelse(pct_correct < reg_pct_correct, 
                               "red", "black"),
          schools = factor(schools, levels = ord_school$school)) 

```



```{r line_pct_correct, dev = "cairo_pdf"}
line_pct_correct(avg_pct_line_graph)
```

\newpage

**Graph 2. Average Percent Correct - Homeroom Comparison**  
This graph compares average percent correct by grade level homerooms across schools. The vertical line represents the grade level average.  
```{r homeroom_level_data}

ord_grade <- assess_summary_hr_reg %>%
  dplyr::filter(grade_level == params$grade) %>%
  group_by(school) %>%
  arrange(school, home_room) %>%
  ungroup() %>%
  select(home_room) %>%
  unique()

home_rm_data <- assess_summary_hr_reg %>%
  dplyr::filter(grepl(params$subject, local_assessment_id),
                grade_level == params$grade) %>% #params$grade
  mutate(avg_pct_correct = round(pct_correct * 100,1),
         grade_pct_correct = round(grade_pct_correct * 100, 1),
         dot_color_c = ifelse(avg_pct_correct < grade_pct_correct,
                                  "red", "black"),
         home_room = factor(home_room, levels = ord_grade$home_room))


            
```


```{r homeroom_comparison, dev = "cairo_pdf"}
home_room_avg(home_rm_data)

```

\newpage

```{r homerooms}
list_homerooms <- assess_summary_hr_reg %>%
  dplyr::filter(grepl(params$subject, local_assessment_id),
                school == params$school, #params$school
                grade_level == params$grade) %>% #params$grade
  select(home_room) %>%
  unique()
```


**Graph 3. Standards Mastered Grade Level View**  
This graph displays the mastery level of students for each standard.  
```{r hist_student_names, fig.height=15, dev = "cairo_pdf"}
list_standards <- stds_school_reg %>%
  dplyr::filter(grepl(params$subject, local_assessment_id),
                school == params$school, #params$school
                grade_level == params$grade) %>%
  select(custom_code) %>%
  arrange(custom_code) %>%
  unique()

stds_mastery_grade_data <-
  student_stds %>%
  dplyr::filter(grepl(params$subject, local_assessment_id),
                school_abbrev == params$school, #params$school
                grade_level == params$grade #params$grade
                #grepl("Fisk", home_room) #for all homerooms
               ) %>%
  mutate(mastered_level = factor(mastered_level,
                                 levels = c("Mastered",
                                            "Near Mastery",
                                            "Partially",
                                            "Not Yet Mastered"))) %>%
  tidyr::unite(firstlast,
               first_name,
               last_name,
                sep = " ") %>%
  mutate(firstlast = str_c(first_name, last_name, sep = " ")) 
# %>%      # moved until after middle name join
  # group_by(home_room,
  #          custom_code,
  #          mastered_level) %>%
  # unique() %>%
  # mutate(pct_rank = row_number(pct_correct))


middle_name_join <- function(file) {
  repeats <- file %>%
    group_by(local_student_id, firstlast) %>%
    summarize() %>%
    ungroup() %>%
    select(-local_student_id) %>%
    count(firstlast) %>%
    filter(n > 1)
  
  if(nrow(repeats) > 0) {
    file <- file %>%
      filter(firstlast == repeats$firstlast) %>%
      mutate(middlefirstlast = str_c(first_name, middle_name, last_name, sep = " "))
  } else {
    file <- repeats %>%
      rbind(file)
  }

  return(file)

}

middle_name_join_file <- middle_name_join(stds_mastery_grade_data)
# added to catch students in same homeroom with same first and last name


stds_mastery_grade_data <- stds_mastery_grade_data %>%
  left_join(middle_name_join_file %>% 
              select(local_student_id, middlefirstlast), 
            by = "local_student_id") %>% 
  mutate(firstlast = ifelse(is.na(middlefirstlast), firstlast, middlefirstlast)) %>% 
  select(-middlefirstlast) %>%
  group_by(#home_room, 
           teacher_name,
           custom_code, 
           mastered_level) %>%
  unique() %>%
  mutate(pct_rank = row_number(percent_correct))

# Added 1/23/20 MAKE SURE IT WORKS



n_stds <- nrow(list_standards)
pages <- ceiling(n_stds / 4)
cut_off <- ceiling(n_stds/pages)

print_hr_stds_table <- function(stds_cut_off, home_room){
cat(sprintf("**%s - %sth Grade** \n ", params$school, params$grade),
    sprintf("**%s** \n ", home_room), sep = "\n")
print(stds_mastered_grade_level(stds_mastery_grade_data %>%
                            dplyr::filter(custom_code %in% list_standards$custom_code[1:stds_cut_off]),
                          home_room))
cat("\\newpage")
cat("\n")

if(n_stds > stds_cut_off &
   n_stds < stds_cut_off*2){
  cat(sprintf("**%s - %sth Grade** \n ", params$school, params$grade),
    sprintf("**%s Continued** \n ", home_room), sep = "\n")
  print(stds_mastered_grade_level(stds_mastery_grade_data %>%
                            dplyr::filter(custom_code %in% list_standards$custom_code[(stds_cut_off+1):n_stds]),
                            home_room))
   }

if(n_stds >= (stds_cut_off*2)){
cat(sprintf("**%s - %sth Grade** \n ", params$school, params$grade),
    sprintf("**%s Continued** \n ", home_room), sep = "\n")
  print(stds_mastered_grade_level(stds_mastery_grade_data %>%
                            dplyr::filter(custom_code %in% list_standards$custom_code[(stds_cut_off+1):(stds_cut_off*2)]),
                            home_room))

cat("\\newpage")
cat("\n")
} 


if(n_stds > (stds_cut_off*2) &
     n_stds <= (stds_cut_off*3)){
cat(sprintf("**%s - %sth Grade** \n ", params$school, params$grade),
    sprintf("**%s Continued** \n ", home_room), sep = "\n")
  print(stds_mastered_grade_level(stds_mastery_grade_data %>%
                            dplyr::filter(custom_code %in% list_standards$custom_code[((stds_cut_off*2)+1):n_stds]),
                            home_room))
cat("\\newpage")
cat("\n")
  } else if(n_stds > (stds_cut_off*3)){
    cat(sprintf("**%s - %sth Grade** \n ", params$school, params$grade),
    sprintf("**%s Continued** \n ", home_room), sep = "\n")
  print(stds_mastered_grade_level(stds_mastery_grade_data %>%
                            dplyr::filter(custom_code %in% list_standards$custom_code[((stds_cut_off*2)+1):(stds_cut_off*3)]),
                            home_room))
cat("\\newpage")
cat("\n")
  }

 if(n_stds > (stds_cut_off*3) &
     n_stds <= (stds_cut_off*4)){
cat(sprintf("**%s - %sth Grade** \n ", params$school, params$grade),
    sprintf("**%s Continued** \n ", home_room), sep = "\n")
  print(stds_mastered_grade_level(stds_mastery_grade_data %>%
                            dplyr::filter(custom_code %in% list_standards$custom_code[((stds_cut_off*3)+1):n_stds]),
                            home_room))
cat("\\newpage")
cat("\n")
 }else if(n_stds > (stds_cut_off*4)){
    cat(sprintf("**%s - %sth Grade** \n ", params$school, params$grade),
    sprintf("**%s Continued** \n ", home_room), sep = "\n")
  print(stds_mastered_grade_level(stds_mastery_grade_data %>%
                            dplyr::filter(custom_code %in% list_standards$custom_code[((stds_cut_off*3)+1):(stds_cut_off*4)]),
                            home_room))
cat("\\newpage")
cat("\n")
  }
  
if(n_stds >= (stds_cut_off*5)){
cat(sprintf("**%s - %sth Grade** \n ", params$school, params$grade),
    sprintf("**%s Continued** \n ", home_room), sep = "\n")
  print(stds_mastered_grade_level(stds_mastery_grade_data %>%
                            dplyr::filter(custom_code %in% list_standards$custom_code[((stds_cut_off*4)+1):n_stds]),
                            home_room))
cat("\\newpage")
cat("\n")
 }
}


```

```{r, results = 'asis', fig.height=15, dev = "cairo_pdf"}
list_homerooms$home_room %>% 
purrr::walk(~print_hr_stds_table(cut_off, .x))

```
\newpage

**Graph 4. Standards Mastered Homeroom View**  
<!-- **`r params$school` - `r list_homerooms$home_room[1]`**     -->
This graph displays students' mastery level of assessment standards by homeroom. The number of standards not mastered can be easily identified.  
```{r, dev = "cairo_pdf"}

print_color_map <- function(home_room_name){
number_mastered <- stds_mastery_grade_data %>%
  dplyr::filter(grepl(params$subject, local_assessment_id),
                home_room == home_room_name) %>%
  group_by(student_id, firstlast, mastered_level) %>%
  summarise(total_mastered = n()) %>%
  tidyr::spread(key = mastered_level,
                value = total_mastered)

name_ord_0 <-  stds_mastery_grade_data %>%
  dplyr::filter(grepl(params$subject, local_assessment_id),
                home_room == home_room_name) %>%
  ungroup() %>%
  select(custom_code, firstlast, mastered_level, student_id) %>% 
  mutate(m_level_2 = case_when(
    mastered_level == "Mastered" ~ 3,
    mastered_level == "Near Mastery" ~ 2,
    mastered_level == "Partially" ~ 1, 
    TRUE ~ 0
  )) %>%
  select(-mastered_level) %>% 
  tidyr::spread(custom_code, m_level_2)

ss_colnames_0 <- grep("CCSS|DLM|SCI", colnames(name_ord_0))

ss_colnames_1 <- colnames(name_ord_0)[ss_colnames_0]

name_ord_1 <- name_ord_0 %>% 
  arrange_(.dots = paste("desc(", ss_colnames_1, ")")) %>%
  select(firstlast)

cat(sprintf("**%s - %s** \n", params$school, home_room_name), sep = "\n")

print(student_mastery_homeroom(number_mastered, stds_mastery_grade_data, 
                         order_db = name_ord_1, colnames_db = ss_colnames_1)) 
cat("\\newpage")
cat("\n")
}
```

```{r, results = 'asis', dev = "cairo_pdf"}
list_homerooms$home_room %>% 
purrr::walk(~print_color_map(.x))

```


